### 2013-07-31 6/conclusional_discussion.tex
Final changes before submission to Alan???

The research sets out to seek the solution for the dual-problem of 
1) establishing scalar and representative statistical models for the multi-dimensional and inter-correlated POLSAR data 
and 
2) developing novel additive and homoskedastic measures of distance for both SAR and POLSAR data, which allow the benefits of the homoskedastic statistical estimation framework to be demonstrated. 
After different scalar statistical models, together with many different data processing techniques, is reviewed for both SAR and POLSAR data,
  chapter \ref{chap:lit_survey} highlights the needs for scalar, representative and homoskedastic statistical models for the multi-dimensional, complex and heteroskedastic data.

  Chapter \ref{chap:sar} then presents homoskedastic models that are derived for heteroskedastic SAR data. 
In chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated POLSAR data.
These two seemingly disconnected results are unified, when the statistical models for POLSAR are shown to be the generic multi-dimensional extension of the commonly used statistical models for SAR intensity.
This combination give rise to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
These theoretical results are applied in chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.

@@

In \textbf{summary}, to address the dual-problem stated earlier, this thesis proposes several
scalar, additive and homoskedastic models for the multi-dimensional, multiplicative
and heteroskedastic POLSAR data. 
The dis-similarity measures are computed for the determinant of the POLSAR covariance matrix,
  which when converted into one-dimensional data
  is gracefully transformed into the traditional SAR intensity.
The models are shown to be theoretically powerful.
Not only they include the one-dimensional SAR under their natural coverage 
they are also able to provide alternative and simpler explanations to a range of theoretical concepts. 
Consequently, these measures of dis-similarity may be employed in a wide range of applications
  where a scalar number is required to represent the complex multi-dimensional POLSAR data.
The proposed theoretical models are also versatile in practice
  as they cope well with imperfect conditions evident in real-life captured data.

@@

\begin{enumerate}
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing}
\end{enumerate}

@@

%How to exploit the advantages of these new results? What
%                are their benefit? And
%                to whom? OK, assuming your solution is novel and it can
%                hold water, is it useful? How is it better than the
%                state-of-the-art? And to whom does this matter? Why
%                should they use your solutions instead of other?
The over-arching strategic benefit is to enable the application of existing and established techniques from one matured field into another less-than-developed new field.
An example is between the fields of SAR and POLSAR, where obviously the SAR data is studied in much further details than the newly derived POLSAR data.
%As is shown, the one-dimensional SAR neatly falls into the limit special case of the multi-dimensional POLSAR.
By putting both SAR and POLSAR into one consistent theory, this thesis opens up the opportunities to apply many of the existing SAR processing technique to POLSAR.
Another example is between the fields of computer science and SAR-based remote sensing.
Evidently while the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
And the proposed homoskedastic models, together with the consistent measures of distance,  %a solution for the second problem
could potentially allows this currently small portion to grow larger.
%a plethoria number of digital image processing algorithms as well as artificial intelligence and machine learning techniques to be applicable for both SAR and POLSAR data.

%Speaking from the author's experience since he first being introduced to this field, the solution for these problem should be important for the next generation of new-comers to the field of (POL)SAR.
%This should also be interesting for experienced experts in the field %as it will increase our capabilities in understanding and processing of (POL)SAR data.
The proposed homoskedastic statistical estimation framework provides a firm foundation
to overcome the various negative impacts of heteroskedasticity on statistical estimations.
This
                is demonstrated in both stages of developing new
                statistical estimators (e.g. speckle filters) as well as evaluating their estimating performance.
Specifically
                in the context of SAR speckle filters: consistent
                variance and homoskedasticity is shown to help in
                breaking the vicious circle of speckle filtering.

@@

Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}, 
new detection, classification, clustering or speckle filtering algorithms can be derived using the models proposed.

@@

While
                the proposed models may have certain limitations, its
                potentials still mostly stays undiscovered.
Since
                the assumptions of partial and full monostatic POLSAR
                models are quite minimal, they are probably also
                applicable to other types of SAR-based data such as: Interferrometric SAR (InSAR), Polarimetric Interferrometric SAR (POLINSAR) 
                or bistatic POLSAR data.
In addition, further experiments can be done to determine whether some existing SAR data processing techniques for SAR can be equally applicable to POLSAR data.
%                Also,
%                it may be interesting time to choose some existing data
%                processing techniques for SAR and showing them
%                applicable to POLSAR data.

@@

@@

\begin{figure}[h!]
\centering
	\subfloat[Original image's histogram and PSF]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
 		 \epsffile{images/log_PSF_NTU_gray_histogram.eps}
		 \label{fig:noise_pdf_as_psf:conv_inputs}
	} 
	\hfill
	\subfloat[Convoluted and speckled image histogram]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_convoluted_NTU_speckled_histogram.eps} 	
		 \label{fig:noise_pdf_as_psf:conv_output_observable}
	}
\caption{Observable convolution of PSF}
\label{fig:noise_pdf_as_psf}
\end{figure}

>>>>

The research sets out to seek the solution for the dual-problem of 
1) establishing scalar and representative statistical models for the multi-dimensional and inter-correlated POLSAR data 
and 
2) developing novel additive and homoskedastic measures of distance for both SAR and POLSAR data, which allow the benefits of the homoskedastic statistical estimation framework to be demonstrated. 
After different scalar statistical models, together with many different data processing techniques, are reviewed for both SAR and POLSAR data,
  Chapter \ref{chap:lit_survey} highlights the needs for scalar, representative and homoskedastic statistical models for the multi-dimensional, complex and heteroskedastic data.

  Chapter \ref{chap:sar} then presents homoskedastic models that are derived for heteroskedastic SAR data. 
In Chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated POLSAR data.
These two seemingly disconnected results are unified, when the statistical models for POLSAR are shown to be the generic multi-dimensional extension of the commonly used statistical models for SAR intensity.
This combination leads to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
These theoretical results are applied in chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.

@@

In summary, to address the dual-problem stated earlier, this thesis proposes several
scalar, additive and homoskedastic models for the multi-dimensional, multiplicative
and heteroskedastic POLSAR data. 
The dis-similarity measures are based on the determinant of the POLSAR covariance matrix,
  which when converted into one-dimensional data
  is gracefully transformed into the traditional SAR intensity.
The models are shown to be theoretically powerful.
Not only they include the one-dimensional SAR under their natural coverage, 
they are also able to provide alternative and simpler explanations to a range of theoretical concepts. 
Consequently, these measures of dis-similarity may be employed in a wide range of applications
  where a scalar number is required to represent the complex multi-dimensional POLSAR data.
The proposed theoretical models are also versatile in practice
  as they cope well with imperfect conditions evident in real-life captured data.

@@

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing}
\end{enumerate}

@@

%How to exploit the advantages of these new results? What
%                are their benefit? And
%                to whom? OK, assuming your solution is novel and it can
%                hold water, is it useful? How is it better than the
%                state-of-the-art? And to whom does this matter? Why
%                should they use your solutions instead of other?
The over-arching strategic benefit is to enable the application of existing and established techniques from one matured field into another less-than-developed new field.
An example is between the fields of SAR and POLSAR, where obviously the SAR data is studied in much further details than the newly derived POLSAR data.
%As is shown, the one-dimensional SAR neatly falls into the limit special case of the multi-dimensional POLSAR.
By putting both SAR and POLSAR into one consistent theory, this thesis opens up the opportunities to apply many of the existing SAR processing technique to POLSAR.
Another example is between the fields of computer science and SAR-based remote sensing.
Evidently the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
And the proposed homoskedastic models, together with the consistent measures of distance,  %a solution for the second problem
could potentially allows this currently small portion to grow larger.
%a plethoria number of digital image processing algorithms as well as artificial intelligence and machine learning techniques to be applicable for both SAR and POLSAR data.

%Speaking from the author's experience since he first being introduced to this field, the solution for these problem should be important for the next generation of new-comers to the field of (POL)SAR.
%This should also be interesting for experienced experts in the field %as it will increase our capabilities in understanding and processing of (POL)SAR data.
The proposed homoskedastic statistical estimation framework also provides a firm foundation
to overcome the various negative impacts of heteroskedasticity on statistical estimations.
This
                is demonstrated in both stages of developing new
                statistical estimators (e.g. speckle filters) as well as evaluating their estimating performance.
Specifically
                in the context of SAR speckle filters: consistent
                variance and homoskedasticity is shown to help in
                breaking the vicious circle of speckle filtering.

@@

Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}, new algorithms can be derived using the proposed models.

@@

Although
                the proposed models may have certain limitations, its
                potentials still mostly stays undiscovered.
Since
                the assumptions of partial and full monostatic POLSAR
                models are quite minimal, they are probably also
                applicable to other types of SAR-based data such as: Interferrometric SAR (InSAR), Polarimetric Interferrometric SAR (POLINSAR) 
                or bistatic POLSAR data.
In addition, further experiments can be done to determine whether some existing SAR data processing techniques for SAR can be equally applicable to POLSAR data.
%                Also,
%                it may be interesting time to choose some existing data
%                processing techniques for SAR and showing them
%                applicable to POLSAR data.

@@

\begin{figure}[ht]
\centering
	\subfloat[Original image's histogram and PSF]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
 		 \epsffile{images/log_PSF_NTU_gray_histogram.eps}
		 \label{fig:noise_pdf_as_psf:conv_inputs}
	} 
	\hfill
	\subfloat[Convoluted and speckled image histogram]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_convoluted_NTU_speckled_histogram.eps} 	
		 \label{fig:noise_pdf_as_psf:conv_output_observable}
	}
\caption{Observable convolution of PSF}
\label{fig:noise_pdf_as_psf}
\end{figure}

@@
